---
title: "Initial Water"
author: "Jackie"
date: "2023-10-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## SA sites



```{r lib, message=FALSE, warning=FALSE, include=FALSE}

#install.packages("tidyverse")
library(tidyverse)
#library(tidyr)
library(dplyr)
library(readr)
library(stringr)
library(lubridate)
```




```{r import data for Roseworthy, message=FALSE, warning=FALSE, include=FALSE}
## import data
site <- "Roseworthy_top_up"
df <- read.csv(paste0("X:/Summer_weeds/APSIM_7/SA_sites/output_csv/", site, "extra_Clm_step2.csv"))
names(df)

```



 


#### Soil options  include:
* Pale Sand
* Loam	
* ClayLoam	
* Clay	
* SandyDuplex

#### Weed type options  include:
* summer grass
* winter dicot


#### Weed density options  include:
* 1,2,7,10,12,15,20,30,50


#### Weed kill options  include:
* 10,15,20,25,30,40,50,60,200

#### Weed sow date options  include:
* 01-Dec
* 01-Jan
* 01-Feb
* 01-Mar

Note that these are the start of the weed sowing window - there is no end date.

#### Capturing if a weed emerged in the same month as the start of the weed sowing window
Is by using the "weed_sow_and_emergedate_month" column.

a) Converted the APSIM output Weed_emergedate, which is a day of the year into a date (coding 0 to NA)
b) Extract the month from the DATE the Weed emerged.
c) Extract the month from the Weed sow date, which is the start of the sowing window.

If the month the weed emerged = the month of the start of the sowing window, then assign the month of the sowing window.


```{r subset Roseworthy data, message=FALSE, warning=FALSE, include=FALSE}

Roseworthy_all_soil_uncontrolled_weeds <- df %>%
  filter(weed_type == "summer_grass") %>%
  # filter(weed_sow_and_emergedate_month == "Feb") %>%
  filter(
    weed_sow_and_emergedate_month == "Dec" |
      weed_sow_and_emergedate_month == "Jan" |
      weed_sow_and_emergedate_month == "Feb" |
      weed_sow_and_emergedate_month == "Mar" 
  ) %>%
  filter(weed_density == 10) %>%
  filter(weed_kill == 200) 
  

unique(Roseworthy_all_soil_uncontrolled_weeds$soil)
unique(Roseworthy_all_soil_uncontrolled_weeds$weed_type)
unique(Roseworthy_all_soil_uncontrolled_weeds$weed_sow_date)
unique(Roseworthy_all_soil_uncontrolled_weeds$weed_density)
unique(Roseworthy_all_soil_uncontrolled_weeds$weed_kill)
unique(Roseworthy_all_soil_uncontrolled_weeds$initial_water)

```

```{r subset Roseworthy data summary, message=FALSE, warning=FALSE, include=FALSE}

Roseworthy_all_soil_uncontrolled_weeds_summary <-
  Roseworthy_all_soil_uncontrolled_weeds %>%
  group_by(soil, initial_water, weed_sow_and_emergedate_month) %>%
  summarise(
    Av_weed_biomass =  mean(Weed_biomass, na.rm = TRUE),
    Av_weed_yield =    mean(Wheat_yield, na.rm = TRUE),
    Av_NO3 =           mean(sownNO3_60, na.rm = TRUE)
  )


Roseworthy_all_soil_uncontrolled_weeds_summary <- ungroup(Roseworthy_all_soil_uncontrolled_weeds_summary)
```
# Plot

```{r subset Roseworthy data plots 1, echo=FALSE, message=FALSE, warning=FALSE}

Roseworthy_all_soil_uncontrolled_weeds_summary$soil <- factor(Roseworthy_all_soil_uncontrolled_weeds_summary$soil, levels = c("PaleSand", "Loam", "ClayLoam", "Clay", "Duplex"))


### Biomass
Roseworthy_all_soil_uncontrolled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_weed_biomass, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Roseworthy uncontrolled weeds",
       subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "weed biomass kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Roseworthy_uncontrolled_biomass_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)


### Yield
Roseworthy_all_soil_uncontrolled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_weed_yield, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Roseworthy uncontrolled weeds",
       subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "wheat yield kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Roseworthy_uncontrolled_yld_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)


### SownNO3  
Roseworthy_all_soil_uncontrolled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_NO3, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Roseworthy uncontrolled weeds",
       subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "No3 top 60cm kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Roseworthy_uncontrolled_No3_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)



```

```{r subset Roseworthy data subset controlled2, echo=FALSE, message=FALSE, warning=FALSE}


Roseworthy_all_soil_controlled_weeds <- df %>%
  filter(weed_type == "summer_grass") %>%
  # filter(weed_sow_and_emergedate_month == "Feb") %>%
  filter(
    weed_sow_and_emergedate_month == "Dec" |
      weed_sow_and_emergedate_month == "Jan" |
      weed_sow_and_emergedate_month == "Feb" |
      weed_sow_and_emergedate_month == "Mar" 
  ) %>%
  filter(weed_density == 10) %>%
  filter(weed_kill == 10) 


  
```



```{r subset Roseworthy data summary2, message=FALSE, warning=FALSE, include=FALSE}

Roseworthy_all_soil_controlled_weeds_summary <-
  Roseworthy_all_soil_controlled_weeds %>%
  group_by(soil, initial_water, weed_sow_and_emergedate_month) %>%
  summarise(
    Av_weed_biomass =  mean(Weed_biomass, na.rm = TRUE),
    Av_weed_yield =    mean(Wheat_yield, na.rm = TRUE),
    Av_NO3 =           mean(sownNO3_60, na.rm = TRUE)
  )


Roseworthy_all_soil_controlled_weeds_summary <- ungroup(Roseworthy_all_soil_controlled_weeds_summary)
```


```{r subset Roseworthy data plots 2d, echo=FALSE, message=FALSE, warning=FALSE}

Roseworthy_all_soil_controlled_weeds_summary$soil <- factor(Roseworthy_all_soil_controlled_weeds_summary$soil, levels = c("PaleSand", "Loam", "ClayLoam", "Clay", "Duplex"))


### Biomass
Roseworthy_all_soil_controlled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_weed_biomass, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Roseworthy controlled weeds",
       subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "weed biomass kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Roseworthy_controlled_biomass_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)


### Yield
Roseworthy_all_soil_controlled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_weed_yield, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Roseworthy controlled weeds",
       subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "wheat yield kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Roseworthy_controlled_yld_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)


### SownNO3  
Roseworthy_all_soil_controlled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_NO3, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Roseworthy controlled weeds",
       subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "No3 top 60cm kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Roseworthy_controlled_No3_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)



```
  