---
title: "Initial Water"
author: "Jackie"
date: "2023-10-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## SA sites



```{r lib, message=FALSE, warning=FALSE, include=FALSE}

#install.packages("tidyverse")
library(tidyverse)
#library(tidyr)
library(dplyr)
library(readr)
library(stringr)
library(lubridate)
```




```{r import data for Minnipa, message=FALSE, warning=FALSE, include=FALSE}
## import data
site <- "Minnipa_top_up"
df <- read.csv(paste0("X:/Summer_weeds/APSIM_7/SA_sites/output_csv/", site, "extra_Clm_step2.csv"))
names(df)

```




 


#### Soil options  include:
* Pale Sand
* Loam	
* ClayLoam	
* Clay	
* SandyDuplex

#### Weed type options  include:
* summer grass
* winter dicot


#### Weed density options  include:
* 1,2,7,10,12,15,20,30,50


#### Weed kill options  include:
* 10,15,20,25,30,40,50,60,200

#### Weed sow date options  include:
* 01-Dec
* 01-Jan
* 01-Feb
* 01-Mar

Note that these are the start of the weed sowing window - there is no end date.

#### Capturing if a weed emerged in the same month as the start of the weed sowing window
Is by using the "weed_sow_and_emergedate_month" column.

a) Converted the APSIM output Weed_emergedate, which is a day of the year into a date (coding 0 to NA)
b) Extract the month from the DATE the Weed emerged.
c) Extract the month from the Weed sow date, which is the start of the sowing window.

If the month the weed emerged = the month of the start of the sowing window, then assign the month of the sowing window.


```{r subset Minnipa data, message=FALSE, warning=FALSE, include=FALSE}

Minnipa_all_soil_uncontrolled_weeds <- df %>%
  filter(weed_type == "summer_grass") %>%
  # filter(weed_sow_and_emergedate_month == "Feb") %>%
  filter(
    weed_sow_and_emergedate_month == "Dec" |
      weed_sow_and_emergedate_month == "Jan" |
      weed_sow_and_emergedate_month == "Feb" |
      weed_sow_and_emergedate_month == "Mar" 
  ) %>%
  filter(weed_density == 10) %>%
  filter(weed_kill == 200) 
  

unique(Minnipa_all_soil_uncontrolled_weeds$soil)
unique(Minnipa_all_soil_uncontrolled_weeds$weed_type)
unique(Minnipa_all_soil_uncontrolled_weeds$weed_sow_date)
unique(Minnipa_all_soil_uncontrolled_weeds$weed_density)
unique(Minnipa_all_soil_uncontrolled_weeds$weed_kill)
unique(Minnipa_all_soil_uncontrolled_weeds$initial_water)

```





```{r subset Minnipa data summary, message=FALSE, warning=FALSE, include=FALSE}

Minnipa_all_soil_uncontrolled_weeds_summary <-
  Minnipa_all_soil_uncontrolled_weeds %>%
  group_by(soil, initial_water, weed_sow_and_emergedate_month) %>%
  summarise(
    Av_weed_biomass =  mean(Weed_biomass, na.rm = TRUE),
    Av_weed_yield =    mean(Wheat_yield, na.rm = TRUE),
    Av_NO3 =           mean(sownNO3_60, na.rm = TRUE)
  )


Minnipa_all_soil_uncontrolled_weeds_summary <- ungroup(Minnipa_all_soil_uncontrolled_weeds_summary)
```


```{r subset Minnipa data subset controlled2, echo=FALSE, message=FALSE, warning=FALSE}


Minnipa_all_soil_controlled_weeds <- df %>%
  filter(weed_type == "summer_grass") %>%
  # filter(weed_sow_and_emergedate_month == "Feb") %>%
  filter(
    weed_sow_and_emergedate_month == "Dec" |
      weed_sow_and_emergedate_month == "Jan" |
      weed_sow_and_emergedate_month == "Feb" |
      weed_sow_and_emergedate_month == "Mar" 
  ) %>%
  filter(weed_density == 10) %>%
  filter(weed_kill == 10) 


  
```



```{r subset Minnipa data summary2, message=FALSE, warning=FALSE, include=FALSE}

Minnipa_all_soil_controlled_weeds_summary <-
  Minnipa_all_soil_controlled_weeds %>%
  group_by(soil, initial_water, weed_sow_and_emergedate_month) %>%
  summarise(
    Av_weed_biomass =  mean(Weed_biomass, na.rm = TRUE),
    Av_weed_yield =    mean(Wheat_yield, na.rm = TRUE),
    Av_NO3 =           mean(sownNO3_60, na.rm = TRUE)
  )


Minnipa_all_soil_controlled_weeds_summary <- ungroup(Minnipa_all_soil_controlled_weeds_summary)
```




# Plot 

```{r subset Minnipa data plots 1, echo=FALSE, message=FALSE, warning=FALSE}

Minnipa_all_soil_uncontrolled_weeds_summary$soil <- factor(Minnipa_all_soil_uncontrolled_weeds_summary$soil, levels = c("PaleSand", "Loam", "ClayLoam", "Clay", "Duplex"))


### Biomass
Minnipa_all_soil_uncontrolled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_weed_biomass, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Minnipa uncontrolled weeds",
       #subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "weed biomass kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Minnipa_uncontrolled_biomass_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)


### Yield
Minnipa_all_soil_uncontrolled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_weed_yield, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Minnipa uncontrolled weeds",
       #subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "wheat yield kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Minnipa_uncontrolled_yld_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)


### SownNO3  
Minnipa_all_soil_uncontrolled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_NO3, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Minnipa uncontrolled weeds",
       #subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "No3 top 60cm kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Minnipa_uncontrolled_No3_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)



```

```{r subset Minnipa data plots 2d, echo=FALSE, message=FALSE, warning=FALSE}

Minnipa_all_soil_controlled_weeds_summary$soil <- factor(Minnipa_all_soil_controlled_weeds_summary$soil, levels = c("PaleSand", "Loam", "ClayLoam", "Clay", "Duplex"))


### Biomass
Minnipa_all_soil_controlled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_weed_biomass, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Minnipa controlled weeds",
       #subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "weed biomass kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Minnipa_controlled_biomass_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)


### Yield
Minnipa_all_soil_controlled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_weed_yield, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Minnipa controlled weeds",
       #subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "wheat yield kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Minnipa_controlled_yld_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)


### SownNO3  
Minnipa_all_soil_controlled_weeds_summary %>% 
ggplot( aes(x=as.factor(initial_water), y = Av_NO3, colour = as.factor(weed_sow_and_emergedate_month)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Minnipa controlled weeds",
       #subtitle = "Weed type  = summer_grass,  \nweed density = 12, weed kill = 200",
       x= "inital water", y = "No3 top 60cm kg/ha",
       colour = "Weed window")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Minnipa_controlled_No3_top_up.png",
       path= "X:/Summer_weeds/APSIM_7/SA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)



```




```{r min and max values, message=FALSE, warning=FALSE, include=FALSE}
#max and min vaues for 2 df


Minnipa_all_soil_uncontrolled_weeds_summary <- Minnipa_all_soil_uncontrolled_weeds_summary %>% mutate(grouping = "uncontrolled_weeds")

Minnipa_all_soil_controlled_weeds_summary <- Minnipa_all_soil_controlled_weeds_summary %>% mutate(grouping = "controlled_weeds")

Minnipa_all_soil_uncontrolled_and_controlled_weeds_summary <- rbind(Minnipa_all_soil_uncontrolled_weeds_summary,
                                                                    Minnipa_all_soil_controlled_weeds_summary)

Minnipa_all_soil_uncontrolled_and_controlled_weeds_summary <- ungroup(Minnipa_all_soil_uncontrolled_and_controlled_weeds_summary)


summary_stats <- Minnipa_all_soil_uncontrolled_and_controlled_weeds_summary %>% 
  group_by(grouping) %>% 
  summarise(min_NO3 = min(Av_NO3),
            max_NO3 = max( Av_NO3),
            
            min_weed_biomass = min(Av_weed_biomass),
            max_weed_biomass = max( Av_weed_biomass),
            
            min_weed_yld = min(Av_weed_yield),
            max_weed_yld = max( Av_weed_yield)
            
            )
summary_stats

min_No3 = summary_stats[1,1]
max_No3 = summary_stats[1,2]

min_weed_biomass = summary_stats[1,3]
max_weed_biomass = summary_stats[1,4]

min_weed_yld = summary_stats[1,5]
max_weed_yld = summary_stats[1,6]


write.csv(summary_stats, 
       "X:/Summer_weeds/APSIM_7/SA_sites/plots/Minnipa_summary_stats_plotted_av.csv")
       
```