---
title: "Initial_Water"
author: "Jackie"
date: "2023-10-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## WA sites



```{r lib, message=FALSE, warning=FALSE, include=FALSE}

#install.packages("tidyverse")
library(tidyverse)
#library(tidyr)
library(dplyr)
library(readr)
library(stringr)
library(lubridate)
```


## Import WA data

```{r import data for katanning, message=FALSE, warning=FALSE, include=FALSE}
## import data
site <- "Katanning"
df <- read.csv(paste0("X:/Summer_weeds/APSIM_7/WA_sites/output_csv/", site, ".csv"))
names(df)

```

# Subset the data 

## Katanning 
soil = Pale Sand, ClayLoam, Clay, SandyDuplex
Weed type  = summer_grass
weed sow date = 01-Dec
weed density = 12
weed kill = 30

### Other soil options  include:
Loam	
ClayLoam	
Clay	
SandyDuplex

### Other weed type options  include:
summer_grass
*should be winter dicot (but I don't think it ran as factorial or imported data had a problem)*

### Other weed sow date options  include:
01-Jan
01-Feb
01-Mar
*(but I don't think it ran as factorial or imported data had a problem)*

### Other weed density options  include:
1,2,7,10,12,15,20,30,50

*(but I don't think it ran as factorial - I have 1,10,12)*

### Other weed kill options  include:
10,15,20,25,30,40,50,60,200

(but got all factorials)

```{r subset katanning data, message=FALSE, warning=FALSE, include=FALSE}

Katanning_all_soil_subset <- df %>% 
  filter(weed_type == "summer_grass") %>% 
  filter(weed_sow_date == "01-Dec") %>% 
  filter(weed_density == 10) %>% 
  filter(weed_kill == 40) 
  

unique(Katanning_all_soil_subset$soil)
unique(Katanning_all_soil_subset$weed_type)
unique(Katanning_all_soil_subset$weed_sow_date)
unique(Katanning_all_soil_subset$weed_density)
unique(Katanning_all_soil_subset$weed_kill)
unique(Katanning_all_soil_subset$initial_water)

```



# Plot

```{r subset katanning data plots of Iitital water and yield, echo=FALSE, message=FALSE, warning=FALSE}

Katanning_all_soil_subset$soil <- factor(Katanning_all_soil_subset$soil, levels = c("PaleSand", "Loam", "ClayLoam", "Clay", "Duplex"))

Katanning_all_soil_subset %>% 
ggplot( aes(x=as.factor(year), y = Weed_biomass, colour = as.factor(initial_water)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Katanning",
       subtitle = "Weed type  = summer_grass, weed sow date = 01-Dec, weed density = 12, weed kill = 30",
       x= "year", y = "weed biomass kg/ha",
       colour = "Initial water")+
  theme(
    axis.text.x = element_text(angle = 90))
 


Katanning_all_soil_subset %>% 
  ggplot( aes(x=as.factor(year), y = Wheat_yield, colour = as.factor(initial_water)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Katanning",
       subtitle = "Weed type  = summer_grass, weed sow date = 01-Dec, weed density = 12, weed kill = 30",
       x= "year", y = "Yield biomass kg/ha",
       colour = "Initial water")+
  theme(    axis.text.x = element_text(angle = 90))
  


```
