---
title: "Initial_Water"
author: "Jackie"
date: "2023-10-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## WA sites



```{r lib, message=FALSE, warning=FALSE, include=FALSE}

#install.packages("tidyverse")
library(tidyverse)
#library(tidyr)
library(dplyr)
library(readr)
library(stringr)
library(lubridate)
```




```{r import data for Merredin, message=FALSE, warning=FALSE, include=FALSE}
## import data
site <- "Merredin_reset_water_yes"
df <- read.csv(paste0("X:/Summer_weeds/APSIM_7/WA_sites/output_csv/", site, "extra_Clm_step2.csv"))
names(df)

```



 


#### Soil options  include:
* Palse sand
* Loam	
* ClayLoam	
* Clay	
* SandyDuplex

#### Weed type options  include:
* summer grass
* winter dicot


#### Weed density options  include:
* 1,2,7,10,12,15,20,30,50


#### Weed kill options  include:
* 10,15,20,25,30,40,50,60,200

#### Weed sow date options  include:
* 01-Dec
* 01-Jan
* 01-Feb
* 01-Mar

Note that these are the start of the weed sowing window - there is no end date.

#### Capturing if a weed emerged in the same month as the start of the weed sowing window
Is by using the "weed_sow_and_emergedate_month" column.

a) Converted the APSIM output Weed_emergedate, which is a day of the year into a date (coding 0 to NA)
b) Extract the month from the DATE the Weed emerged.
c) Extract the month from the Weed sow date, which is the start of the sowing window.

If the month the weed emerged = the month of the start of the sowing window, then assign the month of the sowing window.


```{r subset Merredin data, message=FALSE, warning=FALSE, include=FALSE}

Merredin_all_soil_uncontrolled_weeds <- df %>% 
  filter(weed_type == "summer_grass") %>% 
  filter(weed_sow_and_emergedate_month == "Feb") %>% 
  filter(weed_density == 10) %>% 
  filter(weed_kill == 200) 
  

unique(Merredin_all_soil_uncontrolled_weeds$soil)
unique(Merredin_all_soil_uncontrolled_weeds$weed_type)
unique(Merredin_all_soil_uncontrolled_weeds$weed_sow_date)
unique(Merredin_all_soil_uncontrolled_weeds$weed_density)
unique(Merredin_all_soil_uncontrolled_weeds$weed_kill)
unique(Merredin_all_soil_uncontrolled_weeds$initial_water)

```



# Plot

```{r subset Merredin data plots of Iitital water and yield, echo=FALSE, message=FALSE, warning=FALSE}

Merredin_all_soil_uncontrolled_weeds$soil <- factor(Merredin_all_soil_uncontrolled_weeds$soil, levels = c("PaleSand", "Loam", "ClayLoam", "Clay", "Duplex"))


### Biomass
Merredin_all_soil_uncontrolled_weeds %>% 
ggplot( aes(x=as.factor(year), y = Weed_biomass, colour = as.factor(initial_water)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Merredin uncontrolled weeds",
       subtitle = "Weed type  = summer_grass, weed sow + emerged date = Feb, \nweed density = 12, weed kill = 200",
       x= "year", y = "weed biomass kg/ha",
       colour = "Initial water")+
  theme(
    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
    #plot.background = element_rect(fill = "darkolivegreen1"),
    plot.title = element_text(color="black", size=14, face="bold"))

ggsave(
       device = "png",
       filename = "Merredin_uncontrolled_biomass.png",
       path= "X:/Summer_weeds/APSIM_7/WA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)
 

### Yield
Merredin_all_soil_uncontrolled_weeds %>% 
  ggplot( aes(x=as.factor(year), y = Wheat_yield, colour = as.factor(initial_water)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Merredin uncontrolled weeds",
       subtitle = "Weed type  = summer_grass, weed sow + emerged date = Feb, \nweed density = 12, weed kill = 200",
       x= "year", y = "Yield biomass kg/ha",
       colour = "Initial water")+
  theme(    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
            #plot.background = element_rect(fill = "coral1"),
            plot.title = element_text(color="black", size=14, face="bold")
            )
ggsave(
       device = "png",
       filename = "Merredin_uncontrolled_yield.png",
       path= "X:/Summer_weeds/APSIM_7/WA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)

### SownNO3  
Merredin_all_soil_uncontrolled_weeds %>% 
  ggplot( aes(x=as.factor(year), y = sownNO3_60, colour = as.factor(initial_water)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Merredin uncontrolled weeds",
       subtitle = "Weed type  = summer_grass, weed sow + emerged date = Feb, \nweed density = 12, weed kill = 200",
       x= "year", y = "sownNO3_60",
       colour = "Initial water")+
  theme(    axis.text.x = element_text(angle = 90),
            legend.position = "bottom",
            #plot.background = element_rect(fill = "deepskyblue1"),
            plot.title = element_text(color="black", size=14, face="bold")
            )

ggsave(
       device = "png",
       filename = "Merredin_uncontrolled_sownNO3.png",
       path= "X:/Summer_weeds/APSIM_7/WA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)

```

```{r subset Merredin data 2 plots of Iitital water and yield, echo=FALSE, message=FALSE, warning=FALSE}

Merredin_all_soil_controlled_weeds <- df %>% 
  filter(weed_type == "summer_grass") %>% 
  filter(weed_sow_and_emergedate_month == "Feb") %>% 
  filter(weed_density == 10) %>% 
  filter(weed_kill == 10) 
  



Merredin_all_soil_controlled_weeds$soil <- factor(Merredin_all_soil_controlled_weeds$soil, levels = c("PaleSand", "Loam", "ClayLoam", "Clay", "Duplex"))

# biomass
Merredin_all_soil_controlled_weeds %>% 
ggplot( aes(x=as.factor(year), y = Weed_biomass, colour = as.factor(initial_water)))+
  geom_point()+
  facet_wrap(.~soil)+
  theme_bw()+
  labs(title = "Merredin controlled weeds",
       subtitle = "Weed type  = summer_grass, weed sow + emerged date = Feb, \nweed density = 12, weed kill = 10",
       x= "year", y = "weed biomass kg/ha",
       colour = "Initial water")+
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "bottom",
    #plot.background = element_rect(fill = "darkolivegreen3", color = "black", linewidth = 3),
    plot.title = element_text(color="black", size=14, face="bold")
   
    )
    
 ggsave(
       device = "png",
       filename = "Merredin_controlled_biomass.png",
       path= "X:/Summer_weeds/APSIM_7/WA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)
#yield

Merredin_all_soil_controlled_weeds %>%
  ggplot(aes(
    x = as.factor(year),
    y = Wheat_yield,
    colour = as.factor(initial_water)
  )) +
  geom_point() +
  facet_wrap(. ~ soil) +
  theme_bw() +
  labs(
    title = "Merredin controlled weeds",
    subtitle = "Weed type  = summer_grass, weed sow + emerged date = Feb, \nweed density = 12, weed kill = 10",
    x = "year",
    y = "Yield biomass kg/ha",
    colour = "Initial water"
  ) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "bottom",
    #plot.background = element_rect(fill = "coral1", color = "black", linewidth = 3),
    plot.title = element_text(color="black", size=14, face="bold")
      )

ggsave(
       device = "png",
       filename = "Merredin_controlled_yield.png",
       path= "X:/Summer_weeds/APSIM_7/WA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)
#sownNO3_60

Merredin_all_soil_controlled_weeds %>%
  ggplot(aes(
    x = as.factor(year),
    y = sownNO3_60,
    colour = as.factor(initial_water)
  )) +
  geom_point() +
  facet_wrap(. ~ soil) +
  theme_bw() +
  labs(
    title = "Merredin controlled weeds",
    subtitle = "Weed type  = summer_grass, weed sow + emerged date = Feb, \nweed density = 12, weed kill = 10",
    x = "year",
    y = "sownNO3_60",
    colour = "Initial water"
  ) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "bottom",
    #plot.background = element_rect(fill = "deepskyblue1", color = "black", linewidth = 3),
    plot.title = element_text(color="black", size=14, face="bold")
  )
ggsave(
       device = "png",
       filename = "Merredin_controlled_sownNO3.png",
       path= "X:/Summer_weeds/APSIM_7/WA_sites/plots/",
       width=8.62,
       height = 6.28,
       dpi=600
)
```
  